Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
removing TBD: we have already discussed IO much.
Resolve a TBD

\begin{quote}\small\begin{verbatim}
let x = 1 `div` 0 in (x `seq` return x)
      `shouldThrow` anyArithException
\end{verbatim}\end{quote}

\begin{quote}
    TBD:
    \begin{itemize}
        \item
            This code snippet also illustrates how to deal with pure
            functions.
        \item
            {\tt seq} forces the exception.
        \item
            If {\tt x} is in {\tt NFData}, you may want to use {\tt
            deepseq} instead.
        \item
            The following would not work:
\begin{quote}\small\begin{verbatim}
(1 `div` 0) `shouldThrow` anyArithException
\end{verbatim}\end{quote}
        \item
            We think that pure functions that throw exceptions is bad
            API design.
    \end{itemize}
\end{quote}

TBD: Should we propose:
\begin{quote}\small\begin{verbatim}
shouldThrow_ :: (NFData a, Exception e) =>
  a -> (e -> Bool) -> Expectation
\end{verbatim}\end{quote}

>>>>

\begin{quote}\small\begin{verbatim}
evaluate (1 `div` 0) `shouldThrow` anyArithException
\end{verbatim}\end{quote}
